Commutative character sheaves and geometric types for supercuspidal representations

### 2017-04-06 Geometric types.tex
Starting the proof that  CS(Gab) = CSab(G)

\begin{proposition} \label{prop:CSGabab}
Suppose $G$ is a smooth group scheme.  Then the functor $q\ab^* : \CS(G\ab) \to \CSab(G)$ is an equivalence of categories.
\end{proposition}
\begin{proof}
To simplify notation below, set $H=G\der$.
Since the quotient $q : G \to G\ab$ is an $H$-torsor in the fppf topology \cite{demazure:SGA3-VIA}*{Thm. 3.2}, 
it is also an $H$-torsor in the fpqc topology.  It now follows from descent theory that the comparison functor $\Loc(G\ab) \to \Loc_H(G)$ is an equivalence; argue as in \cite{Vistoli:notes}*{Thm 4.46}, for example. \todo{Need to adapt the following proof to the definition of $q\ab^*$.}

>>>>

\begin{proposition} \label{prop:CSGabab}
Suppose $G$ is a smooth group scheme.  Then the functor $q\ab^* : \CS(G\ab) \to \CSab(G)$ is an equivalence of categories.
\end{proposition}
\begin{proof}
%To simplify notation below, set $H=G\der$.
Since the quotient $q : G \to G\ab$ is an $H$-torsor in the fppf topology \cite{demazure:SGA3-VIA}*{Thm. 3.2}, 
it is also an $H$-torsor in the fpqc topology.  
It now follows from descent theory that the comparison functor $L : \Loc(G\ab) \to \Loc_{G\der}(G)$ is an equivalence; argue as in \cite{Vistoli:notes}*{Thm 4.46}, for example. 
Observe that $L$ followed by the forgetful functor $\Loc_{G\der}(G)\to  \Loc(G)$ coincides with $q^*: \Loc(G\ab)\to \Loc(G)$ and that, for $\cs{L}\ab\in \Loc(G\ab)$,  $L(\cs{L}\ab) = (\cs{L}, \nu)$ where $\cs{L} = q^*(\cs{L}\ab)$ and $\nu : m^*\cs{L}  \to p^*\cs{L}$ is an isomorphism, where $m : G\times G\to G$ is  multiplication and $p : G\times  G \to G$ is projection to the second component.

Now set $G^2 \ceq G\times G$;  note that $G^2\ab =  G\ab \times G\ab$ and $G^2\der = G\der \times G\der$. Let $q_2 : G^2 \to G^2\ab$ be the abelianization quotient.  
Let $L_2 : \Loc(G^2\ab) \to \Loc_{G^2\der}(G^2)$ be the comparison functor for the quotient $q^2  : G^2 \to G^2\ab$.

Now consider the category $\CSab'(G)$ of triples $(\cs{L},\nu,\mu)$ where $(\cs{L},\mu)$ is a character sheaf on $G$ and $\nu :  m^*\cs{L} \to p^*\cs{L}$ is an isomorphism
\[
\begin{array}{rcl}
\CS(G\ab) &\to& \CSab'(G) \\
(\cs{L}\ab,\mu\ab) &\mapsto& (L(\cs{L}\ab), L_2(\mu\ab)) = (\cs{L},\nu,\mu),
\end{array}
\]
where
defined by

Let $R :  \Loc_{G\der}(G)\to  \Loc(G\ab)$ be the right adjoint to $L$ and let  $R_2 :  \Loc_{G^2\der}(G^2)\to  \Loc(G^2\ab)$ be the right adjoint to $L_2$.

\todo{Need to adapt the following proof to the definition of $q\ab^*$.}
